### 2022-01-26 manuscript/manuscript.Rmd
Add content to methods and results sections

The quality of the models was then evaluated both numerically and graphically. The numerical assessment was made by computing the following accuracy indices: the mean absolute error (MAE), mean absolute percent error (MAPE) and root mean square error (RMSE). To visualize the agreement between the values predicted by the models and measured by the FP, Bland-Altman plots were drawn. This type of plot is made by plotting the mean of the actual and predicted values on the x axis and their difference on the y axis. Then, the bias was calculated as the mean of these differences and plotted as a continuous horizontal line, and the limits of agreement were defined by bias ± 1.96 standard deviation and plotted as horizontal dashed lines [@Bland1986]. To further test if there were any consistent under- or over-estimation of the values by the models, one-sample *t*-tests were done to check whether the bias were different than zero. Finally, linear regressions were employed to examine if the difference between actual and predicted values were affected by their magnitude, verifying, therefore, whether the prediction was constant throughout the magnitude range that was tested [@Giavarina2015].

@@

Accelerometer-based mechanical loading prediction equations were developed based on linear mixed models. The regression coefficients, R^2^ and accuracy indices of the models derived from accelerometers worn at ankle, lower back and hip, and from the resultant and vertical vectors are presented in Table 1. The R^2^ values for the pGRF models ranged from `r min(GRF_accuracy$R2_cond)` to `r max(GRF_accuracy$R2_cond)`. These values represent a reasonably good prediction accuracy, that is also reflected on the MAPE values between `r myround(min(GRF_accuracy$MAPE) * 100, 1)`\% and `r myround(max(GRF_accuracy$MAPE) * 100, 1)`\%. Despite similar accuracy results achieved by all equations, data from the resultant vector of accelerometers at the hip have shown the lower accuracy error, represented by the smallest MAE (`r myround(hip_GRF_accuracy$MAE, 1)` N), MAPE (`r myround(hip_GRF_accuracy$MAPE * 100, 1)`\%) and RMSE (`r myround(hip_GRF_accuracy$RMSE, 1)` N). Compared to the pGRF models, the pLR equations yielded poorer results. Their R^2^ ranged from `r min(LR_accuracy$R2_cond)` to `r max(LR_accuracy$R2_cond)` and MAPE from `r myround(min(LR_accuracy$MAPE) * 100, 1)`\% to `r myround(max(LR_accuracy$MAPE) * 100, 1)`\%. However, similar to the pGRF models, the best pLR prediction equation in terms of prediction accuracy was the one from the resultant vector of hip-worn accelerometers, with a MAE of `r myround(hip_LR_accuracy$MAE, 1)` N, MAPE of `r myround(hip_LR_accuracy$MAPE * 100, 1)`\% and RMSE of `r myround(hip_LR_accuracy$RMSE, 1)` N.

@@

>>>>

The quality of the models was then evaluated both numerically and graphically. The numerical assessment was made by computing the following accuracy indices: the mean absolute error (MAE), mean absolute percent error (MAPE) and root mean square error (RMSE). Despite the absence of a standard criterion for establishing an acceptable error in mechanical loading prediction, we regarded a MAPE <8\% to be an accurate prediction based on past research [@Fortune2014; @Neugebauer2014; @Ancillao2018, @Veras2020]. To visualize the agreement between the values predicted by the models and measured by the FP, Bland-Altman plots were drawn. This type of plot is made by plotting the mean of the actual and predicted values on the x axis and their difference on the y axis. Then, the bias was calculated as the mean of these differences and plotted as a continuous horizontal line, and the limits of agreement were defined by bias ± 1.96 standard deviation and plotted as horizontal dashed lines [@Bland1986]. To further test if there were any consistent under- or over-estimation of the values by the models, one-sample *t*-tests were done to check whether the bias were different than zero. Finally, linear regressions were employed to examine if the difference between actual and predicted values were affected by their magnitude, verifying, therefore, whether the prediction was constant throughout the magnitude range that was tested [@Giavarina2015].

Lastly, our pGRF and pLR prediction models were compared with a previously published equation by our group [@Veras2020]. As, for the best of our knowledge, there is no mechanical loading prediction equation developed for jumping activies, we chose to compare it with previous models from our group that were validated in a similar sample. The models used in the comparison were the ones predicting pGRF and pLR from both the resultant and vertical vectors of accelerometers worn at lower back and hip. The MAE, MAPE and RMSE were calculated using the values predicted using Veras et al. [@Veras2020] equation.

@@

Accelerometer-based mechanical loading prediction equations were developed based on linear mixed models. The regression coefficients, R^2^ and accuracy indices of the models derived from accelerometers worn at ankle, lower back and hip, and from the resultant and vertical vectors are presented in Table 1. The R^2^ values for the pGRF models ranged from `r min(GRF_accuracy$R2_cond)` to `r max(GRF_accuracy$R2_cond)`, showing that the models can explain at least `r round(min(GRF_accuracy$R2_cond), 1) * 100`\% of the pGRF variance. The observed MAPE values were between `r myround(min(GRF_accuracy$MAPE) * 100, 1)`\% and `r myround(max(GRF_accuracy$MAPE) * 100, 1)`\%, which falls outside of the proposed threshold of 8\%. Nevertheless, these MAPE values are similar to the results usually found in accelerometer-based energy expenditure prediction [@Diniz-Sousa2020], which have widespread use in research. Despite similar accuracy results achieved by all equations, data from the resultant vector of accelerometers at the hip have shown the lower accuracy error, represented by the smallest MAE (`r myround(hip_GRF_accuracy$MAE, 1)` N), MAPE (`r myround(hip_GRF_accuracy$MAPE * 100, 1)`\%) and RMSE (`r myround(hip_GRF_accuracy$RMSE, 1)` N). Compared to the pGRF models, the pLR equations yielded poorer results, which is expected based on past research [@Fortune2014; @Veras2020]. Their R^2^ ranged from `r min(LR_accuracy$R2_cond)` to `r max(LR_accuracy$R2_cond)` and MAPE from `r myround(min(LR_accuracy$MAPE) * 100, 1)`\% to `r myround(max(LR_accuracy$MAPE) * 100, 1)`\%. However, similar to the pGRF models, the best pLR prediction equation in terms of prediction accuracy was the one from the resultant vector of hip-worn accelerometers, with a MAE of `r myround(hip_LR_accuracy$MAE, 1)` N, MAPE of `r myround(hip_LR_accuracy$MAPE * 100, 1)`\% and RMSE of `r myround(hip_LR_accuracy$RMSE, 1)` N.

@@

```{r accuracy_table2, results = "show"}
source(here("tables", "tab2.R"))
tab2
```
